Testing and Isolation Efficacy; Insights from a Simple Epidemic Model

### 2021-01-25 SIR_manuscript.tex
fix tex breakage

In addition to the overall testing intensity, the testing weights for different compartments, and the degree of self-isolation of test-pending and test-confirmed people,
our models will also need to include test specificity and sensitivity, as well as the distribution of times from testing to reporting. 
\jd{This seems weak. Why are we studying \Rnum? What does it cover and what not?}
Here, we focus on the the effect of testing intensity, different levels of testing ``focus'' (from random to highly targeted), and rate of test processing on a single index of epidemiological dynamics, the basic reproduction number $\Rnum$.

@@

The classical SIR model is based on the following implicit assumptions; well-mixed population, homogeneity of the population, exponentially distributed duration of infection and large population size (see, e.g., \cite{keeling2011modeling}). In addition to these standard assumptions, our model, \crefrange{eq1}{eq12}, assumes: (i) there is a single force of infection, $\Lambda$, across all susceptible pools [\jd{This is de-clarifying here; let's drop it: that is, where a susceptible individual moves to does not depend on who infected it], (ii) $\eta_c \leq \eta_w$, i.e., the individuals awaiting test results have a higher transmission probability than the reported individuals. For this analysis, we also assume a perfectly specific test,($p_S=0$). This last assumption 
%% The latter assumption, combined with the assumption that the total population was initially distributed between untested and awaiting for negative test, that is $S_u(0)+S_n(0)=N(0)$ \bmb{I don't think this is what we need: I think we need $S_p(0)=S_c(0)=0$? The previous assumption is awkward because we must have some infected individuals at time 0, and is more than we need (we could start with some $R$ without loss of generality)}, 
reduces the model to 10 equations (equations \ref{eq3} and \ref{eq4} are eliminated).
%% Specifically, when the population is at steady state and the number of infected people is negligible \bmb{do we really need anything other than the previously stated conditions?}, the assumption of perfect specificity results in $S_p=0$ in \cref{eq3} and $d S_c/dt=0$ from \cref{eq4}. Also, since we assumed $S_u+S_n=0$, $S_c=0$ and stays in this state.

>>>>

In addition to the overall testing intensity, the testing weights for different compartments, and the degree of self-isolation of test-pending and test-confirmed people,
our models will also need to include test specificity and sensitivity, as well as the distribution of times from testing to reporting. 
\jd{This seems weak. Why are we studying $\Rnum$? What does it cover and what not?}
Here, we focus on the the effect of testing intensity, different levels of testing ``focus'' (from random to highly targeted), and rate of test processing on a single index of epidemiological dynamics, the basic reproduction number $\Rnum$.

@@

The classical SIR model is based on the following implicit assumptions; well-mixed population, homogeneity of the population, exponentially distributed duration of infection and large population size (see, e.g., \cite{keeling2011modeling}). In addition to these standard assumptions, our model, \crefrange{eq1}{eq12}, assumes: (i) there is a single force of infection, $\Lambda$, across all susceptible pools \jd{This is de-clarifying here; let's drop it: that is, where a susceptible individual moves to does not depend on who infected it}, (ii) $\eta_c \leq \eta_w$, i.e., the individuals awaiting test results have a higher transmission probability than the reported individuals. For this analysis, we also assume a perfectly specific test,($p_S=0$). This last assumption 
%% The latter assumption, combined with the assumption that the total population was initially distributed between untested and awaiting for negative test, that is $S_u(0)+S_n(0)=N(0)$ \bmb{I don't think this is what we need: I think we need $S_p(0)=S_c(0)=0$? The previous assumption is awkward because we must have some infected individuals at time 0, and is more than we need (we could start with some $R$ without loss of generality)}, 
reduces the model to 10 equations (equations \ref{eq3} and \ref{eq4} are eliminated).
%% Specifically, when the population is at steady state and the number of infected people is negligible \bmb{do we really need anything other than the previously stated conditions?}, the assumption of perfect specificity results in $S_p=0$ in \cref{eq3} and $d S_c/dt=0$ from \cref{eq4}. Also, since we assumed $S_u+S_n=0$, $S_c=0$ and stays in this state.
